\documentclass[10pt]{article}
\usepackage[hmarginratio=1:1,top=32mm,columnsep=20pt]{geometry}                       			


\title{Healthcare Data Lake}

\author{
	\textsc{Kendal, Joseph}\\
	\normalsize University of Bristol\\
	\texttt{jk17246@bristol.ac.uk}
	
	\and
	
	\textsc{Sherred, Jago}\\
	\normalsize University of Bristol\\
	\texttt{j.sherred.2019@bristol.ac.uk}
	
	\and
	
	\textsc{Benson, Luke}\\
	\normalsize University of Bristol\\
	\texttt{wr19606@bristol.ac.uk}
	
	\and
	
	\textsc{Liu, Anna}\\
	\normalsize University of Bristol\\
	\texttt{gf19916@bristol.ac.uk}
	
	\and
	
	\textsc{Cismaru, Armand}\\
	\normalsize University of Bristol\\
	\texttt{fz19792@bristol.ac.uk}
}


\begin{document}

\maketitle    


\begin{abstract}

Digital healthcare provided by the NHS in England typically operates in silos. GPs have electronic systems to manage patient care which are distinct from hospital systems which are distinct from the ambulance service, 111, mental health services etc. Each data owner has a wealth of data that, if combined, would generate a more valuable resource than it does in isolation. While there are solutions to integrate this data for direct care purposes, there is no centralised solution to use this data to inform future care or service provisioning. This project is designed to explore the benefits of cloud technologies to produce a prototype secure, scalable health data storage platform that can underpin local healthcare analytics.

\end{abstract}

\section{Overview}
%TODO%

\subsection{Client}
%TODO%
\subsection{Domain}
%TODO%
\subsection{Project}
%TODO%
\subsection{Vision}

\newpage


\section{Requirements}
\subsection{Stakeholders}
\paragraph{Primary stakeholder}
Philip Harfield at Bristol, North Somerset and South Gloucestershire CCG (BNSSG). Philip Harfield is our client, and this software is being developed for him at BNSSG. BNSSG require a piece of software to store healthcare data from various sources to inform clinical and strategic decisions. This means that BNSSG is our primary stakeholder.
\paragraph{Additional stakeholders}
This software will provide services to a number of local healthcare organisations such as NHS trusts and the Healthier Together STP and such all these additional users are secondary stakeholders to this project. These organisations will need to be able to provide healthcare information to the software which will need to be able to load and store the data for future analysis.

\subsection{User stories}
\paragraph{API}
%TODO%
\paragraph{Data lake}
%TODO%
\paragraph{Data catalogue}
%TODO%
\paragraph{ETL \& Console}
%TODO%


\section{Personal Data, Privacy, Security and Ethics Management}
\subsection{GDPR}
\subsection{Security}
\subsection{Ethics}


\section{Architecture}


\section{Development Testing}


\section{Release Testing}


\section{OO Design \& UML}


\end{document}
